---
title: "Juror Risk - Weighted-Average Illusion"
#author: "gcook"
date: Sys.Date()
output: html_document
---

```{r message=FALSE, warning=FALSE, include=FALSE}
####################################################################
# Don't forget to run this
####################################################################
```

```{r}
C <- readr::read_csv(here::here("data", "wai_juror_exp2.csv"))
```


Attention Checks for Exp 2

```{r message=FALSE, warning=FALSE}
#############################################################
#### Data Summary ###########################################
#############################################################
C %>%
  #dplyr::filter(., tolower(Crime) == "sexual offense") %>%
  #dplyr::filter(., RiskEntry == 9) %>%
  #dplyr::group_by(., RiskEntry) %>%
  dplyr::mutate(., CrimeCorr = ifelse(
    tolower(Crime) == "sexual offense", 1, 0)
    ) %>%
  means1(., CrimeCorr ~ Plot + RiskEntry) %>% 
  dplyr::select(., Plot, RiskEntry, n, CrimeCorr) %>% #t() %>% 
  kbl_it(
    caption = "Attention Check: Mean Correct Crime As a Function of Plot and 'RiskEntry' (9 is correct) ")

C %>%
  #dplyr::filter(., FailedChecks == 0) %>%  # keep no failed checks
  #dplyr::filter(., OrderedRisk  == 1) %>% # keep ordered risk
  dplyr::filter(., RiskEntry == 9) %>%
  dplyr::filter(., !is.na(JuryJudge)) %>%
  #dplyr::filter(., exclusion == "include") %>% 
  dim()

C %>%
  #dplyr::filter(., FailedChecks == 0) %>%  # keep no failed checks
  #dplyr::filter(., OrderedRisk  == 1) %>% # keep ordered risk
  dplyr::filter(., RiskEntry == 9) %>%
  dplyr::filter(., !is.na(JuryJudge)) %>%
  #dplyr::filter(., exclusion == "include") %>%
  dplyr::mutate(., id = seq(1, length(id))) %>%
  dplyr::group_by(., Plot) %>%
  dplyr::summarise(.,
                   n = dplyr::n(),
                   RiskEntry_mean = mean(RiskEntry),
                   RiskEntry_med  = median(RiskEntry),
                   RiskEntry_min  = min(RiskEntry),
                   RiskEntry_max  = max(RiskEntry),
                   ) %>% #t() %>% 
  kbl_it(caption = "Attention Check: Mean Reported Risk Entry (both acc and inacc)")
  #means1(., RiskEntry ~ Plot + RiskEntry) %>% 
  #dplyr::select(., Plot, n, RiskEntry, mdn, min, max) %>% t() %>% 
 

###############################################################################
# Estimate scatterplot for average of all Static-99R
# They don't yet know the Actual Data
###############################################################################
C %>%
  #dplyr::filter(., FailedChecks == 0) %>%  # keep no failed checks
  #dplyr::filter(., OrderedRisk  == 1) %>% # keep ordered risk
  dplyr::filter(., RiskEntry == 9) %>%
  dplyr::filter(., !is.na(JuryJudge)) %>%
  #dplyr::filter(., exclusion == "include") %>%
  dplyr::mutate(., id = seq(1, length(id))) %>%
  means1(., AvgScore_Risk ~ Plot) %>%
  dplyr::select(., Plot, n, AvgScore_Risk, mdn, min, max, skew) %>%
  #select(., -mean) %>% 
  t() %>% kbl_it(caption = 
      "Mean Scatterplot Estimate for all Static-99R Scores")


C %>%
  dplyr::filter(., RiskEntry == 9) %>%
  dplyr::filter(., !is.na(JuryJudge)) %>%
  dplyr::select(., Plot, AvgScore_Risk) %>%
  dplyr::filter(., Plot != "None") %>% #view()
  #chisq.test(AvgScore_Risk, C$Plot) 
  t.test(as.numeric(AvgScore_Risk) ~ Plot, paired = F, data = .)

C %>%
  dplyr::filter(., RiskEntry == 9) %>%
  dplyr::filter(., !is.na(JuryJudge)) %>%
  dplyr::select(., Plot, AvgScore_Risk) %>%
  dplyr::filter(., Plot != "None") %>% #view()
  coin::median_test(formula = AvgScore_Risk ~ Plot, data = .)
  
C %>%
  dplyr::filter(., RiskEntry == 9) %>%
  dplyr::filter(., !is.na(JuryJudge)) %>%
  dplyr::select(., Plot, AvgScore_Risk) %>%
  dplyr::filter(., Plot != "None") %>% #view()
  coin::wilcox_test(formula = AvgScore_Risk ~ Plot, data = ., distribution = "exact", conf.int = T)
  
t_obs <- C %>%
  dplyr::filter(., RiskEntry == 9) %>%
  dplyr::filter(., !is.na(JuryJudge)) %>%
  dplyr::select(., Plot, AvgScore_Risk) %>%
  dplyr::filter(., Plot != "None") %>%
  infer::specify(AvgScore_Risk ~ Plot, x = .) %>%
  infer::calculate(stat = "diff in means", order = c("Unweighted", "Weighted"))

C %>%
  dplyr::filter(., RiskEntry == 9) %>%
  dplyr::filter(., !is.na(JuryJudge)) %>%
  dplyr::select(., Plot, AvgScore_Risk) %>%
  dplyr::filter(., Plot != "None") %>%
  infer::specify(AvgScore_Risk ~ Plot, x = .) %>%
  infer::hypothesize(null = "independence") %>%
  infer::generate(reps = 1000, type = "permute") %>%
  infer::calculate(stat = "diff in means", order = c("Unweighted", "Weighted")) %>%
  infer::visualize() + 
  infer::shade_p_value(t_obs, direction = "two-sided")
```


```{r}
C %>%
  #dplyr::filter(., FailedChecks == 0) %>%  # keep no failed checks
  #dplyr::filter(., OrderedRisk  == 1) %>% # keep ordered risk
  dplyr::filter(., RiskEntry == 9) %>%
  dplyr::filter(., !is.na(JuryJudge)) %>%
  #dplyr::filter(., exclusion == "include") %>%
  dplyr::mutate(., id = seq(1, length(id))) %>%
  ggplot(., aes(x = AvgScore_Risk, fill = Plot)) +
  geom_density(alpha = 0.5) + theme_minimal() 


##########################################################################
# Estimate scatterplot for Static-99R for the defendant
# They don't yet know the Actual Data
##########################################################################
C %>%
  #dplyr::filter(., FailedChecks == 0) %>%  # keep no failed checks
  #dplyr::filter(., OrderedRisk  == 1) %>% # keep ordered risk
  dplyr::filter(., RiskEntry == 9) %>%
  dplyr::filter(., !is.na(JuryJudge)) %>%
  #dplyr::filter(., exclusion == "include") %>%
  dplyr::mutate(., id = seq(1, length(id))) %>%
  means1(., Score_Risk ~ Plot) %>% 
  dplyr::select(., Plot, n, mean, mdn, min, max, skew) %>%
  #select(., -Score_Risk) %>% 
  t() %>% kbl_it(caption = 
    "Mean Scatterplot Estimate for Defendant's Static-99R Score")
```

Juror Commitment Decisions

```{r}
# Juror Decision
C %>% 
  #dplyr::filter(., FailedChecks == 0) %>%  # keep no failed checks
  #dplyr::filter(., OrderedRisk  == 1) %>% # keep ordered risk
  dplyr::filter(., CrimeAcc == 1) %>%   # correct crime
  dplyr::filter(., RiskEntry == 9) %>%  # correct risk reported
  dplyr::filter(., !is.na(JuryJudge)) %>% 
  #dplyr::filter(., exclusion == "include") %>%
  dplyr::mutate(., id = seq(1, length(id))) %>%
  #dplyr::select(., Plot, JuryJudge) %>% view()
  dplyr::group_by(., Plot) %>%
  dplyr::summarise(., 
            n = dplyr::n(),
            yes = sum(JuryJudge, na.rm = T),
            mean = yes/n) %>% t() %>% 
  kbl_it(caption = "Commitment Decisions by Condition")

C %>%
  #dplyr::filter(., FailedChecks == 0) %>%  # keep no failed checks
  #dplyr::filter(., OrderedRisk  == 1) %>% # keep ordered risk
  dplyr::filter(., CrimeAcc == 1) %>%   # correct crime
  dplyr::filter(., RiskEntry == 9) %>%  # correct risk reported
  dplyr::filter(., !is.na(JuryJudge)) %>%
  #dplyr::filter(., exclusion == "include") %>%
  dplyr::mutate(., id = seq(1, length(id))) %>%
  means1(., JuryJudge ~ Plot) %>% 
  dplyr::select(., Plot, n, mean, mdn, min, max, skew) %>% t() %>%
  kbl_it(
    caption = "Commitment Decisions by Condition")

# the numeric estimates for risk levels

C %>%
  #dplyr::filter(., FailedChecks == 0) %>%  # keep no failed checks
  #dplyr::filter(., OrderedRisk  == 1) %>% # keep ordered risk
  dplyr::filter(., CrimeAcc == 1) %>%   # correct crime
  dplyr::filter(., RiskEntry == 9) %>%  # correct risk reported
  dplyr::filter(., !is.na(JuryJudge)) %>%
  #dplyr::filter(., exclusion == "include") %>%
  dplyr::mutate(., id = seq(1, length(id))) %>%
  #means1(., JuryJudge ~ Plot) %>% 
  #select(., Plot, n, mean, mdn, min, max, skew) %>%
  #rename(.data, Commit = mean) #%>%
  data_summary(., varname = "JuryJudge", groupnames = c("Plot")) %>%
  ggplot(., aes(x = Plot, y = JuryJudge)) + 
  geom_bar(stat = "identity", 
           #color = "black", 
           position = position_dodge()
           ) + 
  #geom_errorbar(aes(ymin = JuryJudge-sd, ymax=JuryJudge+sd),width = .2,position = position_dodge(.9)) +
  scale_y_continuous(limits = c(0.0, 0.5), n.breaks = 10) + 
  labs(y = "Commitment Decision\n (% Yes)", 
       x = "Plot Communication Format") +
  theme_classic() 

```

MinNumEst

```{r}
C %>%
  dplyr::filter(., CrimeAcc == 1) %>%   # correct crime
  dplyr::filter(., RiskEntry == 9) %>%  # correct risk reported
  dplyr::filter(., !is.na(JuryJudge)) %>%
  dplyr::group_by(., Plot) %>%
  dplyr::summarise(.,
                   MinNum_BRD = mean(MinNumEst),
                   #MinCat_BRD = mean(MinNumEst_2),
                   ) %>%
   kbl_it(
    caption = "Minimum Recidivism Risk Estimate for Beyond Reasonable Doubt")
  

C <- C %>%
  dplyr::mutate(., MinNumEst_2 = gsub(" Risk", "", MinNumEst_2)) %>%
  dplyr::mutate(., MinCat_BRD = factor(
    MinNumEst_2, levels = c("Very Low", 
                            "Below Average",
                            "Average", 
                            "Above Average",
                            "Well Above Average"))
  ) %>% 
  dplyr::mutate(., MinCat_BRD_num = case_when(
    MinCat_BRD == "Very Low" ~ 1,
    MinCat_BRD == "Below Average" ~ 2,
    MinCat_BRD == "Average" ~ 3,
    MinCat_BRD == "Above Average" ~ 4,
    MinCat_BRD == "Well Above Average" ~ 5,
  ))

C %>%
  select(., Plot, MinNumEst, MinCat_BRD_num) %>%
  group_by(., Plot) %>%
  summarize(., corr = cor(MinNumEst, MinCat_BRD_num, 
                          method = "kendall")) %>% 
  kbl_it(caption = "Kendall Correlation 'MinNumEst & MinCat_BRD_num'")
  
count_2_prop <- function(data, group, x) {
  data %>%
    dplyr::group_by(.data[[group]]) %>%
    dplyr::count(.data[[x]]) %>%
    dplyr::mutate(prop = n/sum(n),
                  perc = n/sum(n) * 100
                  )  
}

#C %>% count_2_prop(data = ., "Plot", "MinCat_BRD")

C %>%
  dplyr::filter(., CrimeAcc == 1) %>%   # correct crime
  dplyr::filter(., RiskEntry == 9) %>%  # correct risk reported
  dplyr::filter(., !is.na(JuryJudge)) %>%
  count_2_prop(data = ., "Plot", "MinCat_BRD") %>%
  ggplot(data = ., aes(x = MinCat_BRD, y = prop)) +
  geom_bar(aes(fill = Plot), colour = "black", 
           width = .8, stat = "identity"#, position = "stack"
      ) + coord_flip() + 
  geom_text(aes(x = MinCat_BRD, 
                y = prop,
                label = round(prop,2)
                #label = paste0(round(prop,2), " (", round(perc, 1),"%)")
                , hjust = +1
                         
                         )) +
  facet_wrap(~Plot) + theme_classic() + 
  theme(legend.position = "none") +
  ggtitle("Minimum Recidivism Risk Category for Beyond Reasonable Doubt")

```

Main Plot: Risk Estimates by Plot Communication

```{r}
C %>%
  dplyr::select(., starts_with("RiskNumEst_"))

mean_Levels <- C %>%
  dplyr::mutate(., id = seq(1, length(id))) %>%
  dplyr::group_by(., Plot) %>%
  dplyr::summarise(., across(starts_with(
    "RiskNumEst_"), ~mean(.x, na.rm = T), .names = "{.col}")) %>%
  tidyr::pivot_longer(
    cols = c(RiskNumEst_1, RiskNumEst_2,
             RiskNumEst_3, RiskNumEst_4, RiskNumEst_5), 
    names_to = "Level", 
    values_to = "Risk"
  ) %>% 
  dplyr::mutate(., Level = gsub("RiskNumEst_", "", Level)) %>%
  dplyr::select(., c(Plot, Level, Risk))

summary_Levels <- C %>%
  dplyr::mutate(., id = seq(1, length(id))) %>%
  dplyr::select(., c(id, Plot, 
                     RiskNumEst_1, RiskNumEst_2, RiskNumEst_3, 
                     RiskNumEst_4, RiskNumEst_5)) %>%
  tidyr::pivot_longer(
    cols = c(RiskNumEst_1, RiskNumEst_2, RiskNumEst_3,
             RiskNumEst_4, RiskNumEst_5), 
    names_to = "Level", 
    values_to = "Risk"
  ) %>% 
  dplyr::group_by(., Plot, Level) %>%
  dplyr::summarise(., 
            #Risk = mean(na.omit(Risk)),
            Risk = median(na.omit(Risk)) 
            ) %>%
  dplyr::mutate(., Level = gsub("RiskNumEst_", "", Level))

n_Plot <- C %>%
  dplyr::filter(., CrimeAcc == 1) %>%   # correct crime
  dplyr::filter(., RiskEntry == 9) %>%  # correct risk reported
  dplyr::filter(., !is.na(JuryJudge)) %>%
  dplyr::group_by(., Plot) %>%
  summarise(., n = dplyr::n()
            ) 
#n_Plot

  # plot with ids
x_labels <- c("Well Below Avg.", "Below Avg.", "Average", "Above Avg.", "Well Above Avg.")
cols <- c("black", "blue", "green")
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
               "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cols <- c("#56B4E9", "#009E73", "#CC79A7")
cols <- c("#0072B2", "#E69F00", "#D55E00")
cols <- c("grey", "red", "blue")
cols <- c("#737373", "#FA2D56", "#2D7FFA") #  "#96B3F2", "#F27981")
# The palette with black:
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73",
                "#F0E442", "#0072B2", "#D55E00", "#CC79A7")


#C %>%
#  filter(., exclusion == "include") %>%
#  select(., id, RiskNumEst_1, RiskNumEst_2, RiskNumEst_3,
#         RiskNumEst_4, MinNumEst, MinNumEst_2, MinNumEst_3) %>%
#  view()

risk_plot_exp1 <- C %>%
  #dplyr::filter(., FailedChecks == 0) %>%  # keep no failed checks
  #dplyr::filter(., OrderedRisk  == 1) %>% # keep ordered risk
  #dplyr::filter(., exclusion == "include") %>%
  #dplyr::filter(., Plot %in% c("None")) %>%
  dplyr::filter(., CrimeAcc == 1) %>%   # correct crime
  dplyr::filter(., RiskEntry == 9) %>%  # correct risk reported
  dplyr::filter(., !is.na(JuryJudge)) %>%
  dplyr::mutate(., id = seq(1, length(id))) %>%
  dplyr::select(., -Risk) %>%
  dplyr::filter(., RiskNumEst_1 < 90) %>%
  tidyr::pivot_longer(
    cols = c(RiskNumEst_1, RiskNumEst_2, RiskNumEst_3,
             RiskNumEst_4, RiskNumEst_5), 
    names_to = "Level", 
    values_to = "Risk"
  ) %>% 
  dplyr::mutate(., Level = gsub("RiskNumEst_", "", Level)) %>%
  dplyr::select(., c(id, Plot, Level, Risk)) %>% 
  #group_by(., Plot) %>%
  #mutate(., Level = gsub("RiskNumEst_", "", Level)) %>%
  ggplot(., aes(x = Level, y = Risk, color = Plot)
         ) +
  #geom_line() + 
  geom_jitter(width = .2, height = 1.5, size = 1.5,
              alpha = .5, 
              #shape = 21#,
              #aes(color = Plot)
              ) #+ 
  #geom_line(inherit.aes = T, 
  #          aes(group = id), 
  #          position = position_jitter(seed = 1), 
  #          size = .4, linetype = 2, alpha = 0.8) +
  # the group level line and points

risk_plot_mean <- risk_plot_exp1 + 
  geom_point(data = mean_Levels, inherit.aes = F, 
             alpha = .8, size = 4, shape = 21, 
             aes(x = Level, y = Risk, 
                 #group = Plot, 
                 fill  = Plot), 
             #fill = Plot, #rep(cols,4), 
             color = "black", 
             ) +  
  geom_line(data = mean_Levels, inherit.aes = F, 
            alpha = .5, size = 1.5, #linetype = 4,
            aes(x = Level, y = Risk, 
                group = Plot, 
                color = Plot,
                )
            ) #+
  #scale_color_manual(values = cols) +
  #ggrepel::geom_text_repel(max.overlaps = 100, aes(label = id), size = 3, color = "gray", segment.colour = NA) +

risk_plot_median <- risk_plot_exp1 + 
  geom_point(data = summary_Levels, inherit.aes = F, 
             alpha = .8, size = 4, shape = 21, 
             aes(x = Level, y = Risk, 
                 #group = Plot, 
                 fill  = Plot), 
             #fill = Plot, #rep(cols,4), 
             color = "black", 
             ) +  
  geom_line(data = summary_Levels, inherit.aes = F, 
            alpha = .5, size = 1.5, #linetype = 4,
            aes(x = Level, y = Risk, 
                group = Plot, 
                color = Plot,
                )
            ) #+


risk_plot_mean <- risk_plot_mean +  
  labs(fill = 'Plot',
       y = "Minimum Risk Percentage\n (mean)",
       x = "Categorical Risk Label") +
  scale_x_discrete(labels = x_labels) +
  scale_y_continuous(n.breaks = 20, limits = c(5, 90)) +
  theme_classic() +
  theme(axis.line = 
          element_line(colour = "black", 
                       size = 1, linetype = "solid"),
        axis.title = element_text(size = 14, face = "bold"), 
        axis.text  = element_text(size = 14),
        strip.text.y = element_text(size = 12),
        aspect.ratio = 1/1,
  #      legend.position = "none"
  ) + 
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) 

risk_plot_median <- risk_plot_median +  
  labs(fill = 'Plot',
       y = "Minimum Risk Percentage\n (median)",
       x = "Categorical Risk Label") +
  scale_x_discrete(labels = x_labels) +
  scale_y_continuous(n.breaks = 20, limits = c(5, 90)) +
  theme_classic() +
  theme(axis.line = 
          element_line(colour = "black", 
                       size = 1, linetype = "solid"),
        axis.title = element_text(size = 14, face = "bold"), 
        axis.text  = element_text(size = 14),
        strip.text.y = element_text(size = 12),
        aspect.ratio = 1/1,
  #      legend.position = "none"
  ) + 
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) 

  #scale_fill_manual('Legend Title', 
  #                  values = c('gray', 'green', "blue")
  #                  )

risk_plot_mean
risk_plot_median
gridExtra::grid.arrange(risk_plot_mean, risk_plot_median, ncol = 2)

```


```{r}
C %>%
  #dplyr::filter(., FailedChecks == 0) %>%  # keep no failed checks
  dplyr::filter(., Exp == "Exp 1") %>%
  dplyr::filter(., OrderedRisk  == 1) %>% # keep ordered risk
  dplyr::filter(., CrimeAcc == 1) %>%   # correct crime
  dplyr::filter(., RiskEntry == 9) %>%  # correct risk reported
  dplyr::filter(., !is.na(JuryJudge)) %>%
  #dplyr::filter(., exclusion == "include") %>%
  ggplot(., aes(x = RiskNumEst_1, fill = Plot)) +
  geom_density(alpha = 0.5) + theme_minimal() 


#C %>%
 # dplyr::filter(., Plot == "None") %>%
#hist(C[Plot == "None", "RiskNumEst_1"], breaks = 20)

  #summarise(., across(where(is.numeric), ~ mean(.x, na.rm = TRUE), .names = "{.col}"))


C %>% 
  dplyr::filter(., Exp == "Exp 1") %>%
  dplyr::filter(., CrimeAcc == 1) %>%   # correct crime
  dplyr::filter(., RiskEntry == 9) %>%  # correct risk reported
  dplyr::filter(., !is.na(JuryJudge)) %>%
  #dplyr::filter(., exclusion == "include") %>%
  means1(., RiskNumEst_1 ~ Plot) %>% kbl_it(
    caption = "Commitment Decisions by Condition")

C %>% 
  dplyr::filter(., Exp == "Exp 1") %>%
  dplyr::filter(., exclusion == "include") %>%
  means1(., RiskNumEst_2 ~ Plot) %>% kbl_it(
    caption = "Commitment Decisions by Condition")

C %>% 
  dplyr::filter(., Exp == "Exp 1") %>%
  dplyr::filter(., exclusion == "include") %>%
  means1(., RiskNumEst_3 ~ Plot) %>% kbl_it(
    caption = "Commitment Decisions by Condition")
C %>% 
  dplyr::filter(., Exp == "Exp 1") %>%
  dplyr::filter(., exclusion == "include") %>%
  means1(., RiskNumEst_4 ~ Plot) %>% kbl_it(
    caption = "Commitment Decisions by Condition")

C %>%
  dplyr::filter(., Exp == "Exp 1") %>%
  means1(., RiskNumEst_5 ~ Plot) %>% 
  kbl_it(
    caption = "Commitment Decisions by Condition")
```



```{r echo=FALSE, message=FALSE, warning=FALSE}
#DAT <- read.csv(paste(
#  dat_dir, "/jurorRandValue-1-31-numeric.csv", sep = "/"), 
#  header = T)

#DAT <- DAT[ -c(1,2),]
NC = N[ , grep("NC_", names(N))]
DJ = N[ , grep("DJ",  names(N))]

#DAT <- read.csv(paste(
#  data_dir, "/jurorRandValue-1-31.csv",
#  sep = "/"), header = T)

qual_vars = c("Crime", "Age", "Vote", "Jury", "Educ", 
              "Job", "Income", "Political", "Race", "Sex",
              "JuryJudge", "RiskCheck", "Risk", "RiskValue",
              "PlotType")

#DAT <- DAT[-c(1:2), ] # remove junky first rows

DAT <- DAT %>% 
  dplyr::select(-c(StartDate, Status, IPAddress, Finished,
                   RecordedDate, ResponseId, RecipientLastName,
                   RecipientFirstName, RecipientEmail,
                   ExternalReference,
                   LocationLatitude, LocationLongitude,
                   DistributionChannel,
                   UserLanguage, Name)
                ) %>%
  #  dplyr::mutate(dplyr::across(, ~as.numeric(.))) %>%
  dplyr::mutate(
    subid   = as.numeric(id),
    Minutes = as.numeric(Duration..in.seconds.)/60,
    CrimeAcc = ifelse(Crime == "Sexual Offense", 1, 0),
    DOB     = as.numeric(Age),
    Age     = (2022 - DOB),
    BeyondDoubt  = ifelse(tolower(JuryJudge) == "no", 0, 1),
    RiskCheck_Not_Rem = ifelse(RiskCheck == "Do not remember", 
                               "Not Remember", ""), # clean up
    RiskCheck = ifelse(RiskCheck == "Do not remember", NA,
                       RiskCheck),
    RiskCheck = as.numeric(gsub("% risk", "", RiskCheck)), # clean up
    RiskCheck = ifelse(subid %in% c(15137), 0, RiskCheck), 
    
    RiskValue = as.numeric(gsub("% risk likelihood", "", RiskValue)),#    RiskNum   = ifelse(RiskCheck == ""),
    RiskCheckAcc  = ifelse(
      as.numeric(RiskValue) == as.numeric(RiskCheck), 1, 0),
    RiskCheckDiff = (as.numeric(RiskValue) - as.numeric(RiskCheck)),
    Crime         = ifelse(Crime == "", "NA", Crime),
    
    Political = ifelse(Political == "", "NA", Political),
    Sex       = ifelse(Sex == "", "NA", Sex),
    Race       = ifelse(Race == "", "NA", Race),
    Educ       = ifelse(Educ == "", "NA", Educ),
    Jury       = ifelse(Jury == "", "NA", Jury),
    
#    MinNumEst   = as.numeric(MinNumEst),
 #   MinNumEst_2 = as.numeric(MinNumEst_2),
  #  MinNumEst_3 = as.numeric(MinNumEst_3),
    #RiskVal2Label = as.numeric(RiskVal2Label), # no need to recode
   # RiskNumEst = 0,
    ) %>% 
  dplyr::filter(!is.na(subid))



# reorder
var_order = c("subid", "Age", "DOB", "Vote", "Jury", "Educ", "Job", 
              "Income", "Political", "Race", "Sex", "Minutes", 
              "RiskValue", "RiskEntry", "RiskCheck", "RiskCheckAcc",
              "Crime", "CrimeAcc", "BeyondDoubt")
var_order = c(var_order, names(DAT)[names(DAT) %in% var_order == F])





DAT <- DAT[!is.na(DAT$subid), var_order]
DAT$Sample = "Sample"
kbl_it_table(DAT$Sample, caption = "Sample Size", freq = T, percent = F)$table
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
view(DAT, show = 1)

#DAT %>% dplyr::group_by(RiskValue) 
```


### Identification of Correct Crime and Risk 

```{r echo=FALSE, message=FALSE, warning=FALSE}
kbl_it_table(DAT$Crime, caption = "Crime Identification", percent = F)$table

#histPlot(DAT$RiskCheckAcc)

#view(DAT[,c("subid", "RiskValue", "RiskCheck", "RiskCheckAcc")])

DAT %>% dplyr::summarise(Prob= mean(na.omit(RiskCheckAcc))) %>% 
  kbl_it(caption = "Risk Value Identification")

```


### Time to Complete 


```{r echo=FALSE, message=FALSE, warning=FALSE}
histPlot(DAT$Minutes)
```


### Exclusion?

There are `r true_count(DAT$RiskCheckAcc)` participants who did not select the correct risk value. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

if (do_exclusion) {
# Remove 
DAT2 <- DAT %>% 
  dplyr::filter(
    RiskCheckAcc == 1,
    Minutes < 60
  )
#DAT <- DAT %>% dplyr::filter(RiskCheckAcc == 1)

kbl_it_table(DAT$Crime, caption = "Crime Identification", percent = F)$table
kbl_it_table(DAT$Sample, caption = "Sample Size", freq = T, percent = F)$table
histPlot(DAT$Minutes)
}
```



### Demographics 

```{r echo=FALSE, message=FALSE, warning=FALSE}
kbl_it_table(DAT$Age,   caption = "", freq = T, percent = F)$table
kbl_it_table(DAT$Age,   caption = "", percent = T)$table

kbl_it_table(DAT$Political, caption = "", percent = T)$table
kbl_it_table(DAT$Educ, caption = "", percent = T)$table

kbl_it_table(DAT$Jury, caption = "", percent = T)$table
kbl_it_table(DAT$Race, caption = "", percent = T)$table
kbl_it_table(DAT$Sex,  caption = "", percent = T)$table
#kbl_it_table(DAT$Job, caption = "", percent = T)
#

(table(DAT$Political, DAT$Sex)) %>% kbl_it(caption = "")
round(prop.table(table(DAT$Political, DAT$Sex))*100,1) %>% kbl_it(caption = "Percentages")

(table(DAT$Political, DAT$RiskValue)) %>% kbl_it(caption = "")
#round(prop.table(table(DAT$Political, DAT$RiskValue))*100,1) %>% kbl_it(caption = "Percentages")

(table(DAT$Political, DAT$Race)) %>% kbl_it(caption = "")

```




### Committment Decision: Beyond Reasonable Doubt

```{r echo=FALSE, message=FALSE, warning=FALSE}

DAT %>%
  #dplyr::filter(RiskCheckAcc == 1) %>%
  dplyr::group_by(RiskValue) %>%
  dplyr::summarise(
    BeyondDoubt = round(mean(BeyondDoubt),2),
#    sd = sd(BeyondDoubt),
    n = dplyr::n(),
  ) %>% kbl_it(caption = "Commit ~ Risk Level")

#means(DAT, "BeyondDoubt", by = "RiskValue") %>% kbl_it(caption = "Commit ~ Risk")
means(DAT, "BeyondDoubt", 
      by = c("Sex", "RiskValue")) %>% kbl_it(caption = "Commit ~ Sex & RV")
means(DAT, "BeyondDoubt", by = c("Sex")) %>% kbl_it(caption = "Commit ~ Sex")

means(DAT, "BeyondDoubt", by = c("Political", "RiskValue")) %>% 
  kbl_it(caption = "Commit ~ Pol & RV")
means(DAT, "BeyondDoubt", 
      by = c("Political")) %>% kbl_it(caption = "Commit ~ Political")

means(DAT, "BeyondDoubt", by = c("Race")) %>% kbl_it(caption = "Commit ~ Race")
means(DAT, "BeyondDoubt", by = c("Race", "RiskValue")) %>% kbl_it(caption = "Commit ~ Race")


head(DAT)

```


### Risk Value Provided to Individual

```{r echo=FALSE, message=FALSE, warning=FALSE}
means(DAT, "BeyondDoubt", by = "RiskValue") %>% #[,c("RiskValue", "mean", "mdn")] %>%
  kbl_it(caption = "Commit ~ Risk (by subid)")

if (include_plots) {
ggplot2::ggplot(DAT, 
                ggplot2::aes(x = .data[["RiskValue"]],
                             y = .data[["BeyondDoubt"]]#, 
                             #color = group
                             )) + # asking it to set the color by the variable "group" is what makes it draw three different lines
  ggplot2::ylab("P (Beyond a Reasonable Doubt)") +  ggplot2::xlab("Risk Value") + 
  ggplot2::geom_line(lwd = 2) +
  ggplot2::geom_point() + 
  #ggplot2::theme_classic() +
  theme_ben() +
  ggplot2::ggtitle("Committ ~ RiskValue (by individuals)")
}

# https://stackoverflow.com/questions/12953045/warning-non-integer-successes-in-a-binomial-glm-survey-packages

mod.i = glm_modPlot(formula = "BeyondDoubt ~ RiskValue", 
                data = DAT, 
                title = "Predicted Model Based on Individuals",
                #family = "gaussian",
                family = "binomial",
                #family = "quasibinomial",
                add_plot = T, 
                ylab = "P (Beyond a Reasonable Doubt)", xlab = "Risk Value", 
                point.col = "blue")

if (include_plots) {
gtsummary::tbl_regression(mod.i$model, exponentiate = T)
#mod.i$plot
mod.i$plot.se
}
#m$plot
#m$pred.data
#


```

### Grouped by Risk Value Provided

```{r echo=FALSE, message=FALSE, warning=FALSE}
#m = glm_modPlot(formula = "vs ~ hp", data = mtcars, family = "binomial",
 #               add_plot = T, point.col = "green")

GROUPED <- DAT %>%
  dplyr::filter(RiskCheckAcc == 1) %>%
  dplyr::group_by(RiskValue) %>%
  dplyr::summarise(
    n   = dplyr::n(),
    BeyondDoubt = mean(BeyondDoubt),
    sd   = sd(BeyondDoubt),
    se   = sd(BeyondDoubt)/sqrt(dplyr::n()),
    mdn  = median(BeyondDoubt),
    
  )


library(correlation)
GROUPED %>%
  dplyr::select(RiskValue, BeyondDoubt) %>%
  correlation()

GROUPED %>% kbl_it(caption = "Commit ~ Risk (by Mean Risk Value)")

#means(GROUPED, "BeyondDoubt", by = "RiskValue")[,c("RiskValue", "mean", "mdn", "n")] %>%
#  kbl_it(caption = "Commit ~ Risk (by Mean Risk Value)")


if (include_plots) {
ggplot2::ggplot(GROUPED, 
                ggplot2::aes(x = .data[["RiskValue"]],
                             y = .data[["BeyondDoubt"]]#, 
                             #color = group
                             )) + # asking it to set the color by the variable "group" is what makes it draw three different lines
  ggplot2::geom_line(lwd = 2) +
  ggplot2::ylab("P (Beyond a Reasonable Doubt)") +  ggplot2::xlab("Risk Value") + 
  ggplot2::geom_point() + 
  ggplot2::theme_classic() +
  ggplot2::ggtitle("Committ ~ RiskValue (Mean by Risk Value)")

}

mod.g = glm_modPlot(formula = "BeyondDoubt ~ RiskValue", 
                data = GROUPED, 
                family = "binomial",
                title = "Predicted Model Based on Risk Value Group",
                add_plot = T, 
                ylab = "P (Beyond a Reasonable Doubt)", xlab = "Risk Value", 
                point.col = "blue")


if (include_plots) {
gtsummary::tbl_regression(mod.g$model, exponentiate = T)
#mod.g$plot
mod.g$plot.se
}


#fit logistic regression model
#model <- glm(vs ~ hp, data = mtcars, family = "binomial")
#m = lm(wt ~ vs, data = mtcars)
#names(m$model)[1]

#plot logistic regression curve
#plot(vs ~ hp, data=mtcars, col = "steelblue")
#lines(vs ~ hp, newdata, lwd = 2)
```

### Model Examination

```{r message=FALSE, warning=FALSE}
# https://www.statology.org/logistic-regression-in-r/
```

### Sample Comparison

```{r}
# https://www.statology.org/jaccard-similarity-in-r/
# https://en.wikipedia.org/wiki/Jaccard_index
```


```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(survival)
ovarian = survival::ovarian
head(ovarian)
S1 = with(ovarian, survival::Surv(futime, fustat))
S1
fit1 = survival::survfit(S1)

summary(fit1)

plot(fit1,xlab="t",ylab=expression(hat(S)*"(t)"))
  
          
          
```


```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#https://blogs.uoregon.edu/rclub/2016/04/05/plotting-your-logistic-regression-models/
#mod <- with(DAT, glm(BeyondDoubt ~ RiskValue, family = binomial("logit"))) # factor(sex),
#mod <- with(DAT, glm(BeyondDoubt ~ RiskValue, family = binomial)) # factor(sex),

mod = glm(formula = BeyondDoubt ~ RiskValue, 
    family = "binomial", data = DAT, na.action = "na.exclude")

#anova(mod, test = "Chisq")

# save the coefficient values so we can use them in the equations
b0 <- mod$coef[1] # intercept
X1 <- mod$coef[2]

X1_range <- seq(from = min(DAT$RiskValue), to = max(DAT$RiskValue), by = .01)

a_logits <- b0 + X1 * X1_range
#b_logits <- b0 + X1 * X1_range 

a_probs <- exp(a_logits)/(1 + exp(a_logits))
#b_probs

plot(X1_range, a_probs, 
     ylim = c(0,1),
     type = "l", 
     lwd  = 3, 
     lty  = 2, 
     col  = "blue", 
     xlab = "Risk Value", 
     ylab = "P(Yes)", main = "Probability of having BRD")

# add a horizontal line at p=.5
abline(h = .5, lty = 2)


#library(ggplot2); library(tidyr)
# first you have to get the information into a long dataframe, which is what ggplot likes :)
plot.data <- data.frame(a = a_probs, X1 = X1_range)
plot.data <- tidyr::gather(plot.data, key = group, value = prob, a)
#head(plot.data)


ggplot2::ggplot(plot.data, 
                ggplot2::aes(x = X1, y = prob, color = group)) + # asking it to set the color by the variable "group" is what makes it draw three different lines
  ggplot2::geom_line(lwd = 2) + ggplot2::theme_classic() +
  ggplot2::labs(x = "Risk Value", 
                y = "P(outcome)", title = "Probability of super important outcome") 

```




```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#  kmeans plot example
#  might need tweaking https://stackoverflow.com/questions/50143207/returning-a-ggplot-object-from-a-function
plot_kmeans_pc <- function(feature_matrix, k, pc) {
    matrix_name = deparse(substitute(feature_matrix)) # name of input variable
    pclusters   = stats::kmeans(feature_matrix, k, nstart = 100, iter.max = 100)
    groups      = pclusters$cluster
    
    # project data onto two principle comps
    projected   = stats::predict(pc, newdata = feature_matrix)[,1:2]
    projected_df <- cbind(as.data.frame(projected), cluster = as.factor(groups))
    # plot
    p <- ggplot2::ggplot(projected_df, ggplot2::aes(
      x = PC1, 
      y = PC2, 
      colour = groups)) + 
           ggplot2::geom_point() + ggplot2::ggtitle(matrix_name)

    return(p)
} 
```


### Clean Need for Cognition

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#+4 = very strong agreement
#+3 = strong agreement
#+2 = moderate agreement
#+1 = slight agreement
#0 = neither agreement nor disagreement
#-1 = slight disagreement
#-2 = moderate disagreement
#-3 = strong disagreement
#-4 = very strong disagreement

names(NC) = (gsub("_","", names(NC)))
NC = sapply(NC, FUN = function(x) { 
        car::recode(x, "1=-4; 2=-3; 3=-2; 4=-1; 5=0; 6=1; 7=2; 8=3; 9=4")  } )
nc_reverse = c(3,4,5,7,8,9,12,16,17) # reverse these columns
NC[, nc_reverse] = sapply(NC[, nc_reverse], FUN = function(x) { 
        car::recode(x, "-4=4; -3=3; -2=2; -1=1; 0=0; 1=-1; 2=-2; 3=-3; 4=-4")  } )
NC = data.frame(NC)
DAT$id
NC$subid = DAT$id
NC$Total = sum(NC[1:18])
view(NC)

DAT[, var_order]

means("Total", data = NC)
#reverse_code()

need4cog_clean <- function(df, get.id = NULL, abbrev = "NC", plot = T) {
  NC.cols = names(df)[grep(abbrev, names(df))]
  if (length(NC.cols) > 18) { 
    message(paste0("Warning: There are too many variables. ",
                   "Need for Cognition has only 18 questions and your data frame has ",
                   length(NC.cols)))
  } else {
    if (length(NC.cols) > 0) { # if there are column in the data frame
      nc_vars = paste0("NC", seq(1:18))
      #c("1", "2", "moderately disagree",
      #            "slightly disagree", "neutral", "slight agree", 
      #            "moderately agreem", "strongly agree", "very strongly agree")
      NC = df[, NC.cols]
      NC = sapply(NC, as.numeric)  # make numeric
      # recode values
      NC = sapply(NC, FUN = function(x) { 
        car::recode(x, "1=-4; 2=-3; 3=-2; 4=-1; 5=0; 6=1; 7=2; 8=3; 9=4")  } )

      NC = as.data.frame(NC)
      # rename to question numbers
      names(NC) = paste0(gsub(paste0(abbrev,".*"), abbrev, names(NC)), (1:length(names(NC))))
      
      NC[,nc_vars] = NC[, 1:18] # get new names for raw responses before reverse coding for composite scores
      
      
      if (plot) {
      #  plot(gplot_likert(NC[,nc_vars], title = "NC", 
      #                    points.no.neutral = 8, neutral.point = 0))
      }
      
      # reverse scoring variables
      nc_reverse = c(3,4,5,7,8,9,12,16,17) # reverse these columns
    
      NC[, nc_reverse] = sapply(NC[, nc_reverse], FUN = function(x) { 
        car::recode(x, "-4=4; -3=3; -2=2; -1=1; 0=0; 1=-1; 2=-2; 3=-3; 4=-4")  } )

      ############### big 5 ###########################################################
      #TIPI$extraversion             = rowMeans(TIPI[,names(TIPI)[c(1,6)]])
      #TIPI$agreeableness            = rowMeans(TIPI[,names(TIPI)[c(2,7)]])
      #TIPI$conscientiousness        = rowMeans(TIPI[,names(TIPI)[c(3,8)]])
      #TIPI[,"emotional stability"]  = rowMeans(TIPI[,names(TIPI)[c(4,9)]])
      #TIPI$openness                 = rowMeans(TIPI[,names(TIPI)[c(5,10)]])
      #TIPI$tipi_total_score         = rowMeans(TIPI[,names(TIPI)[1:10]])
      
      if (!is.null(get.id)) { NC <- cbind(subid = df[,get.id], NC) } 
      keep_surveys = append(keep_surveys, names(NC) )  # store the keep var names
      
      names(NC) = tolower(names(NC))

      return(NC)
      
    } else { rm(NC.cols) }
  }
}


```




